\section*{Method}

Our experiment for determining the ideal mixture involves 5 sample mixtures and one control mixture (which will just be salt).
The sample mixtures will have the following volumetric ratio of hemp to salt: 1:1, 2:1, 3:1, 4:1, and 5:1, and will contain a third of the salt of the control mixture. 
The samples of each mixtures will be called sample 1 through 5, respectively.
With consideration for the size of the containers, control sample will have \SI{15}{\ml} of salt.
Thus, each experimental sample will have \SI{5}{\ml} of salt and their respective amount of hemp hurd.
The ice will be grown in small food storage containers in overnight winter conditions.
Once the water inside the containers is fully frozen, each mixture will be applied to the exposed ice surface.
Observations on the performance of the mixtures will be taken for 90 minutes after its application.

There will be 2 different trials for testing each mixture.
Due to constraints in equipment, the deicing effectiveness of each mixture will be measured by visual observation.
The visual observations will be recorded through filming by a camera.
The first trial will look at the performance of each mixture by visually observing their effectiveness with \SI{2}{\mm} thick ice you could expect after a light snowfall.
This includes observing how much ice is melted, the amount of water present after a certain amount of time, and other characteristics that aid in the removal of ice.
The second experiment looks at a worse case scenario where the ice is unquantifiably and unrealisticly thick.
It is expected that no mixture will work effectively with this test, the approximate amount of ice that is melted will be the primary characteristic to observe.